{ cookiecutter.paper_title}

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Modified 'Figures' path
Deleted 'column-specific' settings
Trying to correct jinga2 with braces error

% Graphics path
\graphicspath{{../Figures/}}

%% Column-specific
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

@@

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{%
    %% Author List
    %%
    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
    %% 
    %% List of Institutions
    $^{1}$ {{ cookiecutter.author_affiliation }}
}

>>>>

% Graphics path
\graphicspath{../Figures/}

%% Column-specific

@@

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
    $^{1}$ {{ cookiecutter.author_affiliation }}
}
